CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity Bounds

### 2017-05-10 kernel_embedding_classifier.tex
Add Abstract

\begin{abstract}
	Kernel embedding of probability distributions are a 
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}

	\note{Draft: Introduction will need a more thorough discussion of motivation, related work, theoretical and practical implications, and contribution.}

>>>>

\begin{abstract}
	We propose learning-theoretic bounds for learning the hyperparameters of kernel embeddings in the probabilistic multiclass classification context. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). However, the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain specific knowledge. We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence of its probabilistic predictions. We then prove that expected classification risk can be bounded by using a data dependent Rademacher complexity measure in the probably approximately correct (PAC) framework. We use this bound to propose a scalable kernel learning algorithm for probabilistic multiclass classification. Classification performance is benchmarked on standard UCI datasets. We further apply our proposed kernel learning algorithm to learn feature representations of a deep convolutional network, with improved accuracy as compared to the original network, demonstrating the generality of this approach.
\end{abstract}

@@

Data dependent risk bounds
\section{Introduction}
\label{sec:introduction}

	Kernel embeddings are a principled way to represent probability distributions in a nonparametric setting.

	learning theoretic (be specific and mention PAC)
	(complexity penalty terms that are not data dependent cannot be universally effective) \citep{kearns1997experimental}
